---
title: "OP-Yield: Adaptation of Oliver and Powers (1978) Yield Table"
classoption: landscape
---

## Setting/input values

| Input   |      Values      | Input   |      Value      |
|----------|:-------------:|----------|:-------------:|
| Planting year |  `r Plant.yr()` | Date/time | `r Sys.time()` |
| Planting density (trees per acre) |   `r plant.den()`   | Planting spacing |   `r round(sqrt(43560/plant.den()), 1)`  |
| Site index (ft) |`r si()` | Initial Planting Survival (%) | `r ini.plant.surv()` |
| Maximum SDI |   `r max.sdi()`   | SDI slope |    `r reineke.term()`   |
| Precommercial thinn age | `r pct.age()` | Precommercial thinn target (trees per acre) | `r pct.tgt()` |
| Annual background mortality (%) |    `r bg.mort()`   |  Merchantability limit (inch) |    `r cf.merch.lim()`   |
| Target rotation retention (trees per acre) | `r reten.tgt()` | Growing stock table age | `r GS.Table.Age()` |


## Yield Summary

```{r, echo=FALSE}

TABLE_OUT <- yield.summary.table(OP.tab.cal())
yth1 <- switch(ineq.cf(),
               "Oliver & Powers 0_1"= "Oliver and Powers (1978) Total Stem CF Volume, 1-foot stump",
               "Wensel & Olson 0_1" = "Wensel and Olson (1995) Total Stem CF Volume, 1-foot stump",
               "MacLean&Berger 4_1" = "MacLean and Berger (1976) CF Volume, 4-inch top, 1-foot stump")
yth2 <- switch(ineq.bf(),
                 "Wensel & Olson 8_1" = "Wensel and Olson (1995): Scribner BF Volume 8-inch top, 1-foot stump",
                 "Wensel & Olson 6_1" = "Wensel and Olson (1995): Scribner BF Volume 6-inch top, 1-foot stump",
                 "Wensel & Olson 4_1" = "Wensel and Olson (1995): Scribner BF Volume 4-inch top, 1-foot stump",
                 "MacLean&Berger v_1" = "MacLean and Berger (1976) Scribner BF Volume, 4-inch top, 1-foot stump")

```

* CF Volume equation: `r yth1`
* BF Volume equation: `r yth2`


```{r, echo=FALSE,warning=FALSE}
suppressWarnings(suppressMessages(library("pander")))   # suppress warnings

panderOptions('table.continues', '')
pander(TABLE_OUT, round=1, style = 'rmarkdown', split.table = Inf)

```



## Growing Stock Table

* Age: `r GS.Table.Age()`, Year: `r GS.Table.Age()+Plant.yr()`


```{r, echo=FALSE,warning=FALSE}

GT_TABLE_OUT <- Growing.stock.table(OP.tab.cal(), cf.merch.lim = cf.merch.lim(), Age=GS.Table.Age())
suppressWarnings(suppressMessages(library("pander")))   # suppress warnings

panderOptions('table.continues', '')
pander(GT_TABLE_OUT, split.table = Inf, round=1, style = 'rmarkdown')

```



## Annual Volume Increment

```{r plot1, fig.height=4, echo=FALSE}
p1()
```


## Stand Density Management Diagram

```{r SDMD, fig.height=10, echo=FALSE}
p4()
```




## DMD Stand Summary

```{r, echo=FALSE,warning=FALSE}
suppressWarnings(suppressMessages(library("pander")))   # suppress warnings
SDMDTABLE_OUT <- cbind(data.frame (Age = seq(5, 60, by=5)), SDMD.t1())
panderOptions('table.continues', '')
pander(SDMDTABLE_OUT, split.table = Inf,  round=1, style = 'rmarkdown')

```


## Stand Density

```{r plot2, fig.height=4, echo=FALSE}
p3()
```


## Density by Crown Class

```{r plot3, fig.height=4, echo=FALSE}
p2()
```

## Precommercial Thinning Summary

* Year: `r ifelse(pct.age()>0, pct.age()+Plant.yr(), "No PCT")`


```{r, echo=FALSE,warning=FALSE}

PCT_TABLE_OUT <- PCT.summary.table(OP.tab.cal())
suppressWarnings(suppressMessages(library("pander")))   # suppress warnings

panderOptions('table.continues', '')
pander(PCT_TABLE_OUT, split.table = Inf, round=1, style = 'rmarkdown')

```

