
# Stand Density Management Diagram Report

* Date/time: `r Sys.time()`

#### *Caution!* Please note that this report was made through the proto-version of SDMD App., so the numbers and figure might contain errors.

## Stand Description

```{r, echo=FALSE}

TABLE_OUT <- t1()
SP_REF<-switch(as.numeric(input$ineq), "User Defined", 
                              "Ponderosa pine:	Long and Shaw (2005)",
                              "Ponderosa pine:	Ritchie and Zhang (In Press)",
                              "Ponderosa pine:	Edminster (1988)",
                              "Ponderosa pine:	Cochran and Barrett (1992)",
                              "California mixed-conifer:	Long and Shaw (2012)",
                              "Douglas-fir:	Long et al. (1988)",
                              "White fir:	Zhang et al. (2007)",
                              "Lodgepole pine:	McCarter and Long (1986)")
UNIT <- ifelse(as.logical(input$use.metric),"Metric","English")
REINEKE <- switch(as.numeric(input$ineq),input$reineke.term, 1.6000, 1.7721, 1.66113, 1.7721, 1.600, 1.605, 1.500, 1.600)

if(as.logical(input$use.metric)){ # metric Units
MAX_SDI <- switch(as.numeric(input$ineq),
                  ifelse(input$max.sdi1<=2470 & input$max.sdi1>=741, input$max.sdi1 , 988),
                  1112,
                  988,
                  1013,
                  902,
                  ifelse(!(input$max.sdi6<=1482 & input$max.sdi6>=1112), 1359, input$max.sdi6),
                  1482,
                  1976,
                  1729)
} else{ #  English units
MAX_SDI <- switch(as.numeric(input$ineq),
                  ifelse(input$max.sdi1<=1000 & input$max.sdi1>=300, input$max.sdi1 , 400),
                  450,
                  400,
                  410,
                  365,
                  ifelse(!(input$max.sdi6<=600 & input$max.sdi6>=450), 550, input$max.sdi6),
                  600,
                  800,
                  700)
}
MGT_ZONE <-paste(if (as.numeric(input$ineq==1)) input$mgt.zone1 else if (input$ineq==6) input$mgt.zone6 else c(0.35,0.60), collapse=" ")  

```

* Species and Reference: `r SP_REF`
* Measured unit: `r UNIT`
* Maximum SDI: `r MAX_SDI`
* Reineke's term (slope): `r REINEKE`
* Management Zone: [`r MGT_ZONE`]


## Estimated Stand Attributes

```{r, echo=FALSE,warning=FALSE}
suppressWarnings(suppressMessages(library("pander")))   # suppress warnings
#library(knitr)
#library(kableExtra)
#kable(TABLE_OUT,warning=FALSE)
panderOptions('table.continues', '')
pander(TABLE_OUT, split.table = 100, round=1, style = 'rmarkdown')
#kable(TABLE_OUT, "latex", booktabs = T) %>%
#kable_styling(latex_options = c("striped", "scale_down"))
```


```{r plot, fig.height=9, echo=FALSE}
p1()
```







